---
title: "Shewhart plots in R"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(Shewhart)
```


## Installation

To install from Github you can use the `install_github` command from the `devtools` package:  

```{r, eval=FALSE}
devtools::install_github("castlaboratory/Shewhart")
```

## Usage

### Data

```{r}
cvd_recife <- read_rds(system.file("extdata", package = "Shewhart", file = "recife_2002_covid19.rds"))

cvd_recife %>% glimpse()
```

### GGPLOT

```{r}
shewhart(data = cvd_recife, 
         index_col = data,
         values_col = obitosNovos, 
         locale = "en_US")
```

```{r}
shewhart(data = cvd_recife, 
         index_col = data,
         values_col = obitosNovos, 
         model = "loglog",
         locale = "en_US")
```


### PLOTLY


```{r, eval=FALSE}
shewhart(data = cvd_recife, 
         index_col = data,
         values_col = obitosNovos, 
         locale = "en_US", 
         model = "log",
         type = "plotly")
```

### Autodetect phases  

You can use the 7-point rule with the command `shewhart_7points`

```{r}
phase_dates <- shewhart_7points(data = cvd_recife, 
                                index_col = data, 
                                values_col = obitosNovos)
print(phase_dates)
```

You can get de model using these dates with the command `shewhart_model`

```{r}
shwt_model <- shewhart_model(data = cvd_recife,
                             index_col = data,
                             values_col = obitosNovos, 
                             phase_changes = phase_dates)

shwt_model %>% head()
```

If you already have the dates or the model you can use it to make the plot

```{r}
shewhart(data = cvd_recife, 
         index_col = data,
         values_col = obitosNovos, 
         model = "loglog",
         locale = "en_US",
         phase_changes = phase_dates)


shewhart(data = shwt_model, 
         index_col = data,
         values_col = obitosNovos, 
         model = "loglog",
         locale = "en_US")
```



## Depedencies

this package depends of:

- lubridate (>= 1.8.0),
- tidyverse (>= 1.3.0),
- tibbletime (>= 0.1.6),
- tidymodels (>= 1.0.0),
- pals (>= 1.7),
- scales (>= 1.2.1),
- plotly (>= 4.1)

## Stay Tuned

Please visit the [castlab.org](https://castlab.org) for latest updates and news.
